Carbon bias

### 2015-10-17 Rmd/carbon-bias.Rmd
17/10/2015, second update, see changelog.txt.

```{r, eval = TRUE}
# selection variables
nms1 <- c(colnames(ctabo), "wgt")
nms2 <- colnames(ctabo)
# bvals <- names(box_stats(sample(1:100, 200, replace = TRUE)))
bvals <- "mu"

@@

    # stack raster bins, cropland bins, and landcover set
    s <- stack(list("bin" = gti_bins[[x]], "wgt" = area_wgts[[x]][[1]], 
                    "mask" = lc_union[[x]][[y]], c_pct_diff[[x]][[y]]))
    DT <- na.omit(as.data.table.raster(s))
    setkey(DT, "bin")
    # indexing columns
    #front1 <- data.table("bin" = rep("all", 6), "N" = rep(nrow(DT), 6))
    #front2 <- data.table("bin" = rep("abs", 6), "N" = rep(nrow(DT), 6))
    # stats, overall means
    #m <- cbind(bvals, DT[mask == 1, lapply(.SD, bfn, wgt), .SDcols = nms1])
    #ma <- cbind(bvals, DT[mask == 1, lapply(.SD, bfna, wgt), .SDcols = nms1])
    # stats per bin
    #b <- cbind(bvals, 
    #           DT[mask == 1, lapply(.SD, bfn, wgt), by = bin, .SDcols = nms1])
    #ba <- cbind(bvals, 
    #            DT[mask == 1, lapply(.SD, bfna, wgt), by = bin, .SDcols = nms1])    
    # output
    #odt <- rbind(cbind(front1, mu), cbind(front2, muabs), 
    #             binl[bin][, bin := paste0("a", bin)], 
    #             binl[binabs][, bin := paste0("b", bin)])[, wgt := NULL]

@@

### Extract statistics for supplemental version 
```{r, eval=FALSE}
# cropland area only
a <- extract_stat0(LC, cb_stats, "all", "m")  # mean cropland only 
b <- cbind(V2 = "All", a[, lapply(.SD, mean), by = V1, .SDcols = lev_vec])
setcolorder(a, c(2:1, 3:ncol(a)))
mu <- rbind(a, b)  # bias

@@

#### Bias and accuracy weighted by agricultural area

@@

# ctabo
xl <- c(-0.5, 18)
# yl <- c(-200, 200)
shd <- c(4.5, 10.5, 16.5)

pdf(full_path(p_fig, "carbon_veg_scalew.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
abline(h = yax, v = NULL, col = "grey80", lty = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey50")
for(i in 1:length(lev_vec)) { # i <- 1; j <- 1; k <- 1
  for(j in 1:length(snms)) {
    for(k in 1:length(mutype)) {
      dat <- get(mutype[k])[ol == lev_vec[i] & map == snms[j], LC2, with=FALSE]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      for(z in 1:length(LC2)) {
        lpfunc(x[i] + xo[j] + o[k], dat[, z, with = FALSE], col = "black", 
               size = cx[z], pch = pchs[z], type = "pt")
      }
    }
  }
}
axis(1, at = seq(1.5, 18.5, 3), labels = c(1, fact))
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = -210, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = -210, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = -212, labels = "MAE", srt = 45, adj = c(0, 0), cex = 0.8)
text(x = 12.2, y = -212, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
legend(x = 12.1, y = 260, legend = c("Forest", "Shrubland", "Sparse", "Mean"), 
       pch = pchs, pt.cex = c(2, 1.5, 1.5, 2), bty = "n", cex = 0.8)
dev.off()

#### Agricultural area bias and accuracy

```{r, eval=FALSE}
#yr <- range(all_l[, 3:8, with = FALSE], all_u[, 3:8, with = FALSE])
# yl <- range(all_mus[, 3:8, with = FALSE])

# yl <- range(mu[, 3:8, with = FALSE], mua[, 3:8, with = FALSE])
# yl <- round(yl / 10) * 10
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))

mutype <- c("mua", "mu")

xl <- c(-0.5, 18)
yl <- c(-60, 70)
shd <- c(4.5, 10.5, 16.5)

pdf(full_path(p_fig, "carbon_veg_scale.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
grid(NA, 13, lwd = 1, lty = 1)
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey50")
for(i in 1:length(lev_vec)) {
  for(j in 1:length(snms)) {
    for(k in 1:length(mutype)) {
      dat <- get(mutype[k])[V1 == snms[j] & V2 %in% LC2, get(lev_vec[i])]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      for(z in 1:length(LC2)) {
        lpfunc(x[i] + xo[j] + o[k], dat[z], col = "black", size = cx[z], 
               pch = pchs[z], type = "pt")
      }
    }
  }
}
axis(1, at = seq(1.5, 18.5, 3), labels = c(1, fact))
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = -40, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = -40, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = -42, labels = "MAE", srt = 45, adj = c(0, 0), cex = 0.8)
text(x = 12.2, y = -42, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
legend(x = 12.1, y = 65, legend = c("Forest", "Shrubland", "Sparse", "Mean"), 
       pch = pchs, pt.cex = c(2, 1.5, 1.5, 2), bty = "n", cex = 0.8)
dev.off()

#### Density independent bias and accuracy

```{r, eval=FALSE}
yl <- range(mund[, 3:8, with = FALSE], munda[, 3:8, with = FALSE])
yl <- round(yl / 10) * 10
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))

mutype <- c("munda", "mund")

o <- c(0, w)
pchs <- c("*", "+", "o", "-")
cx <- c(2, 1.25, 1, 1)
g1 <- "grey90"
xl <- c(-0.5, 18)
shd <- c(4.5, 10.5, 16.5)

pdf(full_path(p_fig, "carbon_veg_scale_nd.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
grid(NA, length(yax) - 1, lwd = 1, lty = 1)
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey50")
for(i in 1:length(lev_vec)) {
  for(j in 1:length(snms)) {
    for(k in 1:length(mutype)) {
      dat <- get(mutype[k])[V1 == snms[j] & V2 %in% LC2, get(lev_vec[i])]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      for(z in 1:length(LC2)) {
        lpfunc(x[i] + xo[j] + o[k], dat[z], col = "black", size = cx[z], 
               pch = pchs[z], type = "pt")
      }
    }
  }
}
yll <- -120
axis(1, at = seq(1.5, 18.5, 3), labels = c(1, fact))
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = yll, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = yll, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = yll - 2, labels = "MAE", srt = 45, adj = c(0, 0), cex = 0.8)
text(x = 12.2, y = yll - 2, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
legend(x = 12.1, y = 165, legend = c("Forest", "Shrubland", "Sparse", "Mean"), 
       pch = pchs, pt.cex = c(2, 1.5, 1.5, 2), bty = "n", cex = 0.8)
dev.off()

@@

caption <- paste("Biases and mean absolute errors for each of the cropland", 
                 "maps across aggregation scales and each possible landcover", 
                 "type sharing the pixel with cropland. Means were calculated",
                 "across the entire country.")
mu0s_xtab <- xtable(mu0s[order(Metric, Cover)], digits = 1, caption = caption)
print(mu0s_xtab, type = "latex", file = "paper/figures/C-bias-mean-all-SA.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

# Statistics from non-croplands areas included in means, for supplementals
# mu[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
# mua[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mus <- copy(rbind(cbind(Metric = "Bias", mu), 
                  cbind(Metric = "MAE", mua)))
setnames(mus, c("V1", "V2", lev_vec), 
         c("Map", "Cover", paste(c(1, fact), "km")))
setkeyv(mus, c("Map", "Cover"))
for(i in 1:length(LC)) mus[Cover == LC[i], Cover := pnms[i]]
setkey(mus, "Map")
for(i in 1:length(snms)) mus[Map == snms[i], Map := mcap[i]]

caption <- paste("Biases and mean absolute errors for each of the cropland", 
                 "maps across aggregation scales and each possible landcover", 
                 "type sharing the pixel with cropland. Metrics were calculated",
                 "across the union of agricultural areas", 
                 "(cropland $>$0.05\\%) identified by the reference map and", 
                 "the cropland map to which it was being compared")
mus_xtab <- xtable::xtable(mus[order(Metric, Cover)], digits = 1, 
                           caption = caption)
print(mus_xtab, type = "latex", 
      file = "paper/figures/C-bias-mean-cropland-SA.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

# still to do: tables for density independent biases

# Bind all three tables together
fulls <- rbind(cbind("Region" = "Density weighted", muws), 
               cbind("Region" = "Country", mu0s),
               cbind("Region" = "Agricultural", mus))

caption <- paste("Biases and mean absolute errors for each of the cropland", 
                 "maps across aggregation scales and each possible landcover", 
                 "type sharing the pixel with cropland. Three variants", 
                 "of the bias/accuracy values are provided, indicated by the:",
                 "Region column: 1) weighted by reference cropland density", 
                 "(Density weighted); 2) across the entire country (Country);",
                 "3) for agricultural areas only (Agricultural, i.e.", 
                 "$>$0.05\\% cropland).")
fulls_xtab <- xtable(fulls[order(Region, Metric, Cover)], digits = 1, 
                     caption = caption)
print(fulls_xtab, type = "latex", file = "paper/figures/C-bias-accuracy.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

@@

```{r, eval=FALSE, echo=FALSE}
# Plot means against cropland density (to possibly be run - for now, 
# too much information)
mub <- do.call(rbind, lapply(1:20, function(x) {
  cbind("bin" = x, extract_stat(LC, cb_stats, x, "m"))
}))
muba <- do.call(rbind, lapply(1:20, function(x) {
  cbind("bin" = x, extract_stat(LC, cb_stats, x, "ma"))
}))
n <- do.call(rbind, lapply(1:20, function(x) {
  cbind("bin" = x, N(LC, cb_stats, x, "m"))
}))
#n[, mean(f50), by = bin]

pp <- list("x" = c(-2, 21), "y" = c(0, 0), 
           "x21" = list(c(0, 9), c(9, 21)),
           "y2" = list(c(seq(-100, -10, 10), seq(10, 100, 10)), 
                       seq(10, 100, 10)), 
           "y1lwd" = list(2, 1),  
           "y2lwd" = 0.5, 
           "y2lc" = list(c("black", rep("grey80", 4), "black", rep("grey80", 4),
                           rep("grey80", 4), "black", rep("grey80", 4),"black"),
                         rep("grey80", 10)),
           "yl" = list(c(-100, 100), c(0, 100)), 
           "yl2" = c(-100, 100), "xl" = c(1, 20),
           "xaxl" = unlist(lapply(seq(5, 100, 10), function(x) c(x, " "))),
           "xaxl2" = ifelse(seq(5, 100, 5) %in% c(25, 50, 75), seq(5, 100, 5), 
                            " "),
           "yax1" = list(seq(-100, 100, 50), seq(0, 100, 20)), 
           "ycol" = c("grey70"))  # plot parameters

yax <- seq(-100, 100, 10)
xax <- seq(0, 22, 20 / (length(yax) - 2))

pdf(full_path(p_fig, "carbon_biases_1-100km_v1.pdf"), width = 7.5, height = 7)
par(mfrow = c(6, 4), mar = c(0.5, 0, 0.5, 0.5), mgp = c(1, 0.5, 0), tcl = -0.3,
    oma = c(6, 4, 1, 0))
for(f in 1:length(LC)) {
  for(j in c(1, 4:6)) {#j <- 1; f <- 1
      plot(xax, yax, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
       ylab = "", xlab = "", 
       panel.first = grid(NA, length(yax) - 1, lwd = 1, lty = 1))
      lines(pp$x, pp$y, lwd = 1)
    for(i in 1:4) {
      mub[V1 == snms[i] & V2 == LC[f], 
          lines(get(lev_vec[j]), col = cols[i], lty = 2, lwd = lw)]
      muba[V1 == snms[i] & V2 == LC[f], 
           lines(get(lev_vec[j]), col = cols[i], lty = 1, lwd = lw)]
    }
  }
}
dev.off()

ys <- c(-100, 100)
yax <- seq(ys[1], ys[2], 10)
xax <- seq(0, 22, 20 / (length(yax) - 2))

#yl <- list(c(-100, 100), c(0, 100))
yl <- seq(yax[1], yax[length(yax)], 10)
yll <- as.character(yl)
yll[seq(2, length(yll) - 1, 2)] <- ""
Ccols <- brewer.pal(n = 6, name = "Dark2") 
xaxl = ifelse(seq(5, 100, 5) %in% c(5, 25, 50, 75, 100), seq(5, 100, 5), " ")
x <- mub[V1 == snms[f] & V2 == LC[j], get(lev_vec[i])]
y <- 100
toohigh <- function(x, y, col = "black", yadj = 0, cex = 1.1) {
  h <- which(abs(x) > abs(y))
  if(length(h) > 0) {
    xi <- h[which.max(h)]
    text(xi, y = y + yadj, labels = round(x[xi]), cex = cex, col = col, 
         xpd = NA)
  }
}

pdf(full_path(p_fig, "carbon_biases_1-100km_v2.pdf"), width = 7.5, height = 7)
par(mfrow = c(4, 4), mar = c(0.5, 0, 0.5, 0.5), mgp = c(1, 0.5, 0), tcl = -0.3,
    oma = c(6, 4, 1, 0))
for(f in 1:length(snms)) {
  for(i in c(1, 4:6)) {#i <- 1; j <- 1; f <- 2
      plot(xax, yax, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
           ylab = "", xlab = "", 
           panel.first = grid(NA, (length(yax) - 1) / 2, lwd = 1, lty = 1))
      lines(pp$x, pp$y, lwd = 1)
    for(j in 1:length(LC)) {
      e <- parse(text = "V1 == snms[f] & V2 == LC[j]")
      mub[eval(e), 
          lines(get(lev_vec[i]), col = Ccols[j], lty = 2, lwd = lw)]

      mub[V1 == snms[f] & V2 == LC[j], 
          lines(get(lev_vec[i]), col = Ccols[j], lty = 2, lwd = lw)]
      mub[V1 == snms[f] & V2 == LC[j], toohigh(get(lev_vec[i]), ys[1])]
      muba[V1 == snms[f] & V2 == LC[j], 
           lines(get(lev_vec[i]), col = Ccols[j], lty = 1, lwd = lw)]
      axis(1, at = c(1, 5, 10, 15, 20), labels = rep("", 5), mgp = c(1, 1, 0), 
           tcl = -0.7, lwd.ticks = 1.2, pos = pp$yl2[1])
      axis(1, at = 1:20, labels = rep("", 20), las = 2, mgp = c(1, 0.4, 0), 
           tcl = -0.3, pos = pp$yl2[1])
      if(f == length(snms)) {
        axis(1, at = 1:20, labels = pp$xaxl2, las = 2, mgp = c(1, 0.8, 0), 
             tcl = -0.3, pos = pp$yl2[1])
      }
      if(i == 1) axis(2, at = yl, labels = yll, las = 2, mgp = c(1, 0.6, 0))
      if(i == 1 & j == 1) {
        mtext(lcnms[f], side = 2, line = 2.8, cex = 1, col = cols[f])
      }
    }
  }
}
dev.off()

i1 <- "sa30"; i2 <- "forest"; s1 <- "f1"
mub[V1 == i1 & V2 == i2, ]
mub[V1 == i1 & V2 == i2, plot(bin, f1, type = "l")]
mubin[V1 == i1 & V2 == i2, plot(bin, f1, type = "l")]
```

```{r, eval=FALSE, echo=FALSE}
# Checks on data values (embedded code)
# Carbon values and carbon biases - random selection of cells from c_tab_diff
# compared to recalculated values for those points
i <- c_pct_diff
for(chk in list(c("modmu", "f25", "forest"), c("geow", "f10", "shrub"), 
                c("sa30", "f50", "sparse"))) {
  x <- chk[1] #names(i[[1]])[3]
  y <- chk[2] #names(i)[4]
  tp <- chk[3]
  r <- i[[y]][[x]][[tp]]
  rid <- which(values(Which(r != 0)))
  sid <- sample(rid, 20)
  v1 <- r[sid]  # value to check
  sav <- gti_agg[[y]]$gti[sid]
  lcv <- lc_agg[[y]][[x]][sid]
  c1 <- carbon(sav, cropC = 5, noncropC = ctabo[1, tp])
  c2 <- carbon(lcv, cropC = 5, noncropC = ctabo[1, tp])
  #round((sav * 5) + (ctabo[1, tp] * (1 - sav)), 2) == c1
  #round((lcv * 5) + (ctabo[1, tp] * (1 - lcv)), 2) == c2
  print(all(v1 == (c1 - c2) / c1 * 100))
}  # all true

# Carbon bias by bins 
# DT-derived values
mu0a <- do.call(rbind, lapply(1:20, function(x) {
  cbind("bin" = x, extract_stat(LC, cb_stats, x, "ma0"))
}))
cb_stats$f1$sa30
cb_stats$f10$sa30[get("bin") == 19, ]

# Older variant of code from compare-landcover.Rmd to evaluate whether newer DT
# version is finding correct results
for(chk in list(c("modmu", "f25", "forest"), c("geow", "f10", "shrub"), 
                c("sa30", "f50", "sparse"))) {
  x <- chk[1] #names(i[[1]])[3]
  y <- chk[2] #names(i)[4]
  tp <- chk[3]
  print(paste(".", x, "..", y, "..", tp))
  d1 <- do.call(rbind, lapply(1:(length(binv) - 1), function(j) {
    #print(paste("......bin", j))
    d2 <- do.call(rbind, lapply(tp, function(z) {#:length(i[[y]][[x]]),..
      #print(paste("........variant", z))
      l3 <- abs(i[[y]][[x]][[z]])  # i[[y]][[x]][[z]]
      #print(paste("........vegetation:", names(l3)))
      d3 <- do.call(rbind, lapply(1, function(k) { #:length(l3)...
        rs <- gti_bins[[y]][[1]] == j #[[k]] == j    
        rs[rs == 0] <- NA
        o <- rs * l3 #[[k]]
        w <- area_wgts[[y]][[1]] * rs
        oo <- cbind.data.frame("lc" = rep(paste0(x, y, z), length(w)), 
                               getValues(o), getValues(w))
      }))
      d3f <- d3[!is.na(d3[, 2]), ]
    }))
    if(nrow(d2) > 0) { #(length(i[[x]][[y]]) * 10)) {
      qs <- c(nrow(d2), box_stats(d2[, 2], weighted = TRUE, 
                                  weight.opts = list("weights" = d2[, 3])))
    } else if((nrow(d2) > 0) & (nrow(d2) < length(i[[x]][[y]]) * 20)) {
      qs <- c(rep(NA, 6), Hmisc::wtd.mean(d2[, 2], weights = d2[, 3], 
                                          na.rm = FALSE))
    } else {
      qs <- rep(NA, 7)
    }
  }))
  #print(round(d1[, "mu"], 2) == mubin[V1 == x & V2 == tp, y, with = FALSE], 
  #          na.rm = TRUE)
  #print(all(round(d1[, "mu"], 2) == mubin[V1 == x & V2 == tp, y, with = FALSE], 
  #          na.rm = TRUE))
  print(all(round(d1[, "mu"], 2) == 
              mu0a[V1 == x & V2 == tp, y, with = FALSE], na.rm = TRUE))
}
# all true

# another check of DT-derived stats against a raster-calculated variant
tst <- sapply(names(c_pct_diff)[1], function(x) {
  lapply(names(c_pct_diff[[1]]), function(y) {
    cellStats(c_pct_diff[[x]][[y]]$forest, mean)
  })
})
mean(round(unlist(tst)), 2) == mean(round(mu0[V2 == "forest", f1]), 2)

gti_gt0 <- Which(gti_agg$f1$gti > 0)
lc_gt0 <- calc(stack(lapply(lc_agg$f1, function(x) Which(x > 0))), sum)
all_gt0 <- gti_gt0 + lc_gt0
all_gt0 <- all_gt0 / all_gt0

filts <- sapply(names(c_pct_diff), function(x) {
  gti_gt0 <- Which(gti_agg[[x]]$gti > 0)
  lc_gt0 <- calc(stack(lapply(lc_agg[[x]], function(j) Which(j > 0))), sum)
  all_gt0 <- gti_gt0 + lc_gt0
  all_gt0 <- all_gt0 / all_gt0
})

tst <- sapply(names(c_pct_diff), function(x) {
  lapply(names(c_pct_diff[[x]]), function(y) {
    cellStats(filts[[x]] * c_pct_diff[[x]][[y]]$forest, mean)
  })
})

tstabs <- sapply(names(c_pct_diff), function(x) {
  lapply(names(c_pct_diff[[x]]), function(y) {
    cellStats(abs(filts[[x]] * c_pct_diff[[x]][[y]]$forest), mean)
  })
})

plot(c(1, 6), range(tst, tstabs), pch = "", xlab = )
for(i in 1:nrow(tst)) lines(1:6, tst[i, ], lty = 2)
for(i in 1:nrow(tstabs)) lines(1:6, tstabs[i, ], col = "red")

cellStats(all_gt0 * c_pct_diff$f1$sa30$sparse, mean)
cellStats(all_gt0 * c_pct_diff$f1$sa30$forest, median)
cellStats(c_pct_diff$f1$sa30$forest, mean)
cellStats(all_gt0 * c_pct_diff$f1$sa30$forest, mean)

>>>>

```{r, eval=FALSE}
# selection variables
nms1 <- c(colnames(ctabo), "wgt")
nms2 <- colnames(ctabo)
# bvals <- names(box_stats(sample(1:100, 200, replace = TRUE)))
bvals <- "mu"

@@

    # stack raster bins, cropland bins, and landcover set
    s <- stack(list("bin" = gti_bins[[x]], "wgt" = area_wgts[[x]][[1]], 
                    "mask" = lc_union[[x]][[y]], c_pct_diff[[x]][[y]]))
    DT <- na.omit(as.data.table.raster(s))
    setkey(DT, "bin")

    # Potentially useful material deleted here: check repo prior to 17/10 if
    # needed

@@

### Extract statistics for secondary methods

For supplementals
```{r, eval=FALSE}
# cropland area only
a <- extract_stat0(LC, cb_stats, "all", "m")  # mean cropland only 
b <- cbind(V2 = "All", a[, lapply(.SD, mean), by = V1, .SDcols = lev_vec])
setcolorder(a, c(2:1, 3:ncol(a)))
mu <- rbind(a, b)  # bias

@@

#### Density-weighted bias and accuracy

@@

# ctabo
xl <- c(-0.5, 18)
shd <- c(4.5, 10.5, 16.5)

pdf(full_path(p_fig, "carbon_veg_scalew.pdf"), height = 7, width = 7)
par(mar = rep(1, 4), oma = c(2, 2, 0, 0), mgp = c(1, 0.5, 0), tcl = -0.3)
plot(xl, yl, pch = "", yaxt = "n", xaxt = "n", xaxs = "i", yaxs = "i", 
     ylab = "", xlab = "")#,
for(i in shd) polyfunc2(x = i, y = yl, w = 3, col = g1, bcol = g1, lwd = 1)
abline(h = yax, v = NULL, col = "grey80", lty = 1)
polyfunc2(x = 8.75, y = yl, w = 18.5, col = "transparent", bcol = "black")
lines(c(-1, 18), c(0, 0), lwd = 2, col = "grey50")
for(i in 1:length(lev_vec)) { # i <- 1; j <- 1; k <- 1
  for(j in 1:length(snms)) {
    for(k in 1:length(mutype)) {
      dat <- get(mutype[k])[ol == lev_vec[i] & map == snms[j], LC2, with=FALSE]
      pcol <- makeTransparent(cols[j], alpha = alph[k])
      polyfunc2(xa[j, i] + o[k], range(dat), w = w, col = pcol, bcol = pcol)
      for(z in 1:length(LC2)) {
        lpfunc(x[i] + xo[j] + o[k], dat[, z, with = FALSE], col = "black", 
               size = cx[z], pch = pchs[z], type = "pt")
      }
    }
  }
}
axis(1, at = seq(1.5, 18.5, 3), labels = c(1, fact))
axis(2, at = yax, labels = yax, las = 2)
mtext(side = 1, text = "Resolution (km)", outer = TRUE, line = 0.5)
mtext(side = 2, text = "Bias/MAE (%)", outer = TRUE, line = 1)
legend(x = 12.4, y = -210, legend = lcnms, pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0.5)
legend(x = 11.9, y = -210, legend = rep("", 4), pch = 15, adj = 0, 
       col = makeTransparent(cols, alpha = alph[2]), pt.cex = 1.5, bty = "n", 
       cex = 0.8)
text(x = 12.7, y = -212, labels = "MAE", srt = 45, adj = c(0, 0), cex = 0.8)
text(x = 12.2, y = -212, labels = "Bias", srt = 45, adj = c(0, 0), cex = 0.8)
legend(x = 12.1, y = 260, legend = c("Forest", "Shrubland", "Sparse", "Mean"), 
       pch = pchs, pt.cex = c(2, 1.5, 1.5, 2), bty = "n", cex = 0.8)
dev.off()
```

```{r, echo=FALSE, eval=FALSE}
# Agricultural area bias and accuracy, deleted here. Values in supplmentary table
# Check repo before 17/10/15 to retrieve
```
<a href="#top">Back to top</a>

@@

# Statistics from agricultural areas
mus <- copy(rbind(cbind(Metric = "Bias", mu), 
                  cbind(Metric = "MAE", mua)))
setnames(mus, c("V1", "V2", lev_vec), 
         c("Map", "Cover", paste(c(1, fact), "km")))
setkeyv(mus, c("Map", "Cover"))
for(i in 1:length(LC)) mus[Cover == LC[i], Cover := pnms[i]]
setkey(mus, "Map")
for(i in 1:length(snms)) mus[Map == snms[i], Map := mcap[i]]

# Bind all three tables together
fulls <- rbind(cbind("Region" = "Density", muws), 
               cbind("Region" = "Country", mu0s),
               cbind("Region" = "Agricultural", mus))

caption <- paste("Biases and mean absolute errors for each of the cropland", 
                 "maps across aggregation scales and each possible landcover", 
                 "type sharing the pixel with cropland. Three variants", 
                 "of the bias/accuracy values are provided, indicated by the:",
                 "Region column: 1) weighted by reference cropland density", 
                 "(Density weighted); 2) across the entire country (Country);",
                 "3) for agricultural areas only (Agricultural, i.e.", 
                 "$>$0.05\\% cropland).")
fulls_xtab <- xtable(fulls[order(Region, Metric, Cover)], digits = 1, 
                     caption = caption)
print(fulls_xtab, type = "latex", file = "paper/figures/C-bias-accuracy.tex", 
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE) 
#       add.to.row = list(pos = list(0), 
#                         command = "\\hline \\endhead"))

@@

```{r, eval=FALSE, echo=FALSE}
# Plot means against cropland density, deleted because not used. Check repo
# prior to 17/10/15 if needed. 
```
